---
title: "Main_04_Adipocytes_Fat_1.for annotation"
author: "Jia Nie"
date: "1/13/2022"
output: html_document
---

### DISCLAIMER ---------------------------------------------------------------------------------------------------------------------
Some of the algorithms are non-deterministic making the results slightly different from run to run.
Many of the algorithms are frequently updated with new releases making the results slightly different from version to version.
Depending on your system, this code below may not produce an exact 1:1 copy of the results. 
This adversely affects clustering, filtering etc. if the code is naively copy-pasted.
For better reproducibility, please download quality-filtered Rds objects and work on downstream analyses. 

change "D:/" to "/media/jianie/Extreme SSD1/" # if in LUNIX computer

# Load libraries -------------------------------------------------------------------------------------------------------------
```{r clear background, eval=TRUE, include=FALSE}
# rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.
memory.limit(size = 1e+13)
```

```{r, include=FALSE}
source(paste0(Disk, Project.folder, "/", "Project Parameters.R"), local = knitr::knit_global())
source(paste0(Disk, "00_Functions_Refs/Functions_Human Fat snRNA.R"), local = knitr::knit_global())
# or sys.source("your-script.R", envir = knitr::knit_global())
``` 

```{r install packages, eval=TRUE, include=FALSE}
# library("velocyto.R") # linux -specific
```



# Import data and subset -----------------------------------------------------------------------------------------------------------
```{r}
## Import data and subset ------------------------------------------------------------------------------------------------
eWAT <- readRDS(paste0(Disk, Project.folder, "/", Rds.folder, "/", seurat.file))
file.name <- stringr::str_split(seurat.file, ".Rds")[[1]][1]
Annotation.meta.data <- readRDS(paste0(Disk, Project.folder, "/", Rds.folder, "/", file.name, "_Annotation.metadata.Rds"))  
eWAT <- AddMetaData( object = eWAT, metadata = Annotation.meta.data)
gc() #free up memrory and report the memory usage.

Amb <- readRDS(paste0(Disk, Project.folder, "/", Rds.folder, "/","Ambient.Rds"))
gc() #free up memrory and report the memory usage.
seurat.data <- subset(eWAT, subset = Annotation == "Adipocytes")
rm(eWAT)
gc() #free up memrory and report the memory usage.

celltype.name <- stringr::str_split(celltype.file, ".Rds")[[1]][1]
# Embedding and clustering of Adipocytess into subpopulations  ----------------------------------------------------------------------------------------
# NOTE: THIS STEP IS NON-DETERMINISTIC (Harmony) - RESULTS VARY FROM RUN TO RUN. 
# Thus, in order to reproduce downstream analyses using the same Harmony results, please download eWAT_Adipocytes.Rds
seurat.data <- FindVariableFeatures(seurat.data, nfeatures= 3000) # 1000 in sarvari
VariableFeatures(seurat.data) <- VariableFeatures(seurat.data)[!(VariableFeatures(seurat.data) %in% Amb)]
#all.genes <- rownames(seurat.data)
#seurat.data <- ScaleData(seurat.data, features = all.genes)
gc() #free up memrory and report the memory usage.
seurat.data <- ScaleData(seurat.data)
seurat.data <- RunPCA(seurat.data)
seurat.data <- RunHarmony(seurat.data, group.by.vars="Dataset", assay.use = "originalexp", plot_convergence = TRUE)
gc() #free up memrory and report the memory usage.
ElbowPlot(seurat.data, ndims = 50) # choose dims
# seurat.data <- RunUMAP(seurat.data, dims=1:10, reduction="harmony") # Orignal from Sarvari
# seurat.data <- FindNeighbors(object = seurat.data, dims = 1:10, reduction = "harmony") # Orignal from Sarvari
seurat.data <- RunUMAP(seurat.data, dims=1:20, reduction="harmony")
seurat.data <- FindNeighbors(object = seurat.data, dims = 1:20, reduction = "harmony") 
seurat.data@project.name <- celltype.name
saveRDS(seurat.data, paste0(Disk, Project.folder, "/", Rds.folder, "/", file.name, "_" ,celltype.file))
gc() #free up memrory and report the memory usage.

# save meta data
meta.data <- seurat.data@meta.data
saveRDS(meta.data, paste0(Disk, Project.folder, "/", Rds.folder, "/", file.name, "_", celltype.name, "_basic.meta.data.Rds"))
gc() #free up memrory and report the memory usage.
```


```{r}
rm(Amp, celltype.name, seurat.data, meta.data, Annotation.meta.data)
```

